%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Professional Resume - Projects Section
%
% This file contains the 'Projects' section aligned with portfolio website.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Projects}

\begin{itemize}
    \item 
    \textbf{Sinhala Fact-Checking RAG System} \hfill \textbf{2024 -- Present}\\
    \textit{Python, LangChain, Pinecone, Claude 3.5 Sonnet, OCR, Tesseract, OpenAI Embeddings}
    \begin{itemize}
      \item Built a multi-agent Retrieval-Augmented Generation (RAG) system for detecting Sinhala misinformation from news articles and social media posts.
      \item Designed five specialized agents: Claim Extractor, Language Processor (tokenization, NER, transliteration), Evidence Retriever, Reasoning Agent, and Verdict Generator.
      \item Integrated Pinecone vector database for semantic search over trusted Sinhala news sources; used Claude 3.5 Sonnet for reasoning and verdict generation.
      \item System outputs verdicts (True, False, Partially False, Misleading) with justifications in Sinhala.
      \item \faGlobe\ \href{https://molindu-achintha.github.io/projects/sinhala-fake-news/}{Project Page}
    \end{itemize}

    \item 
    \textbf{Light-Weight 3D Generator for MRI Super-Resolution} \hfill \textbf{July 2024 -- Present}\\
    \textit{PyTorch, MONAI, CUDA, ANTsPy, SimpleITK, Nibabel, NumPy, Matplotlib}
    \begin{itemize}
      \item Developed a novel Wasserstein GAN with Gradient Penalty (WGAN-GP) framework for enhancing low-resolution 3D MRI brain scans to high-resolution volumes.
      \item Designed a lightweight 3D Multi-scale Dense Residual Network (3D-MDRN) generator optimized for medical imaging.
      \item Conduct systematic comparison of perceptual loss paradigms: Swin UNETR (medical specialist) vs DINOv3 (generalist) for optimal feature guidance.
      \item Built robust preprocessing pipeline with skull stripping, bias field correction, and intensity normalization; trained on HCP, IXI, and BraTS datasets.
      \item \faGlobe\ \href{https://molindu-achintha.github.io/projects/3d-mri-super-resolution/}{Project Page}
    \end{itemize}

    \item
    \textbf{Crowdbox AI Quality Assurance Agent} \hfill \textbf{2024 -- Present}\\
    \textit{LangGraph, Claude 3.5 Sonnet, Pinecone, AssemblyAI, AWS Lambda, Salesforce API, Zoom API}
    \begin{itemize}
      \item Designed enterprise multi-agent system for automated SDR call evaluation, achieving 100\% call coverage QA scoring.
      \item Integrated Salesforce CRM and Zoom Workspaces API for call metadata; transcribed calls using AssemblyAI speech-to-text.
      \item Built LangGraph-orchestrated worker agents (Tone, Rapport, Delivery, Compliance) with a Supervisor Agent for scoring aggregation.
      \item Implemented RAG-powered Policy Enforcement Agent using Pinecone vector database for dynamic rubric retrieval.
      \item Developed real-time dashboards for QA admins and agents with Slack/Email escalation alerts.
      \item \faGlobe\ \href{https://molindu-achintha.github.io/projects/ai-qa-agent/}{Project Page}
    \end{itemize}

        \item 
    \textbf{Sinhala Idioms Extraction and Translation} \hfill \textbf{2024}\\
    \textit{Python, PyTorch, Transformers, BERT, Tesseract OCR, NLTK, SpaCy, Pandas}
    \begin{itemize}
      \item Built end-to-end NLP system for detecting English idioms, classifying usage (idiomatic/literal/ambiguous), and mapping to Sinhala equivalents.
      \item Designed BERT-based sequence labeling model for idiom span detection using BIO tagging scheme.
      \item Developed OCR pipeline using Tesseract to extract Sinhala text from scanned books and printed documents.
      \item Created parallel corpus mapping 500+ Sinhala idioms to semantically equivalent English expressions using cross-lingual semantic retrieval.
      \item \faGlobe\ \href{https://molindu-achintha.github.io/projects/sinhala-idioms/}{Project Page}
    \end{itemize}

    \item
    \textbf{Verdex: AI-Powered Crop Disease Identifier} \hfill \textbf{Feb 2024 -- May 2025}\\
    \textit{Flutter, Dart, PyTorch, Flask, AWS EC2, PostgreSQL, Firebase Auth, Amazon S3}
    \begin{itemize}
      \item Developed cross-platform mobile application for Sri Lankan rice farmers to detect crop diseases from leaf images.
      \item Trained MobileNetV2 CNN with transfer learning, achieving 89.3\% accuracy on 4-class disease classification (Brown Spot, Hispa, Leaf Blast, Healthy).
      \item Built Flask backend deployed on AWS EC2 with PostgreSQL database for disease profiles and cultivation plans.
      \item Implemented localized treatment recommendations and multilingual support (Sinhala + English) for 1M+ target farmers.
      \item \faGlobe\ \href{https://molindu-achintha.github.io/projects/verdex/}{Project Page} | \faGithub\ \href{https://github.com/Project-Verdex/Verdex-Mobile.git}{Mobile App} | \href{https://github.com/Project-Verdex/Verdex-Model.git}{ML Model}
    \end{itemize}

    \item 
    \textbf{Diabetic Retinopathy Detection Using Fundus Images} \hfill \textbf{Nov 2024 -- Jan 2025}\\
    \textit{Python, TensorFlow, Keras, Scikit-learn, OpenCV, SMOTE, NumPy, Pandas}
    \begin{itemize}
      \item Trained an ensemble classifier combining InceptionNet and ResNet model outputs for multi-class diabetic retinopathy detection.
      \item Applied SMOTE (Synthetic Minority Oversampling Technique) to handle severe class imbalance in medical imaging dataset.
      \item Implemented comprehensive data augmentation pipeline: rotation, flipping, brightness adjustment, and contrast enhancement.
      \item \faGlobe\ \href{https://molindu-achintha.github.io/projects/diabetic-retinopathy/}{Project Page} | \faGithub\ \href{https://github.com/sandaruwanWGMA/Diabetic-retinopathy-detection-using-fundus-images-V3.git}{GitHub}
    \end{itemize}

    \item
    \textbf{SIIM-ISIC Melanoma Classification Using Transfer Learning} \hfill \textbf{Sep 2024 -- Oct 2024}\\
    \textit{Python, TensorFlow, Keras, EfficientNet B7, OpenCV, Pydicom, Scikit-image}
    \begin{itemize}
      \item Implemented modified EfficientNet B7 architecture with custom classification head for melanoma detection from dermoscopic images.
      \item Built preprocessing pipeline for DICOM medical images: grayscale conversion, Gaussian denoising, CLAHE contrast enhancement, and lesion segmentation.
      \item Applied transfer learning from ImageNet weights with fine-tuning on SIIM-ISIC competition dataset.
      \item \faGlobe\ \href{https://molindu-achintha.github.io/projects/melanoma-classification/}{Project Page} | \faGithub\ \href{https://github.com/sandaruwanWGMA/SIIM-ISIC-Melanoma-Classification-Using-Transfer-Learning.git}{GitHub}
    \end{itemize}

\end{itemize}
